Evolution of the AGN UV luminosity function from redshift 7.5

### 2019-02-25 Paper/paper.tex
Update Table 2
Update

    &
    &
    &
    &
    &
    \multicolumn{1}{c}{cMpc$^{-3}$mag$^{-1}$)} &
    &
    & \\
    \hline
    0.31$^a$ & 0.10 & 0.40 & 3520 & 3632 & -5.62^{+0.09}_{-0.11} & -21.37^{+0.21}_{-0.23} & -2.94^{+0.09}_{-0.10} & -1.22^{+0.18}_{-0.16} \\
    0.50$^a$ & 0.40 & 0.60 & 4555 & 4686 & -6.13^{+0.04}_{-0.04} & -23.00^{+0.08}_{-0.07} & -3.38^{+0.08}_{-0.08} & -1.36^{+0.04}_{-0.04} \\
    0.72 & 0.60 & 0.80 & 3308 & 4684 & -6.42^{+0.09}_{-0.08} & -24.03^{+0.14}_{-0.13} & -3.56^{+0.12}_{-0.13} & -1.75^{+0.04}_{-0.04} \\
    0.91 & 0.80 & 1.00 & 3922 & 5248 & -6.39^{+0.08}_{-0.08} & -24.50^{+0.12}_{-0.12} & -3.69^{+0.11}_{-0.11} & -1.73^{+0.06}_{-0.05} \\
    1.10 & 1.00 & 1.20 & 6367 & 6566 & -6.54^{+0.03}_{-0.03} & -25.15^{+0.04}_{-0.04} & -4.18^{+0.08}_{-0.08} & -1.73^{+0.02}_{-0.02} \\
    1.30 & 1.20 & 1.40 & 6479 & 7132 & -6.42^{+0.04}_{-0.04} & -25.29^{+0.06}_{-0.05} & -3.97^{+0.08}_{-0.08} & -1.74^{+0.03}_{-0.03} \\
    1.50 & 1.40 & 1.60 & 7539 & 7771 & -6.51^{+0.03}_{-0.03} & -25.67^{+0.04}_{-0.04} & -4.28^{+0.08}_{-0.08} & -1.76^{+0.02}_{-0.02} \\
    1.71 & 1.60 & 1.80 & 6788 & 7421 & -6.29^{+0.03}_{-0.03} & -25.56^{+0.05}_{-0.05} & -3.96^{+0.07}_{-0.07} & -1.60^{+0.03}_{-0.03} \\
    1.98 & 1.80 & 2.20 & 10478 & 10876 & -6.72^{+0.03}_{-0.03} & -26.26^{+0.04}_{-0.04} & -4.21^{+0.07}_{-0.07} & -1.87^{+0.02}_{-0.02} \\
    2.30$^a$ & 2.20 & 2.40 & 8419 & 8419 & -6.16^{+0.07}_{-0.06} & -25.49^{+0.12}_{-0.11} & -3.34^{+0.12}_{-0.12} & -1.61^{+0.04}_{-0.04} \\
    2.45$^a$ & 2.40 & 2.50 & 3403 & 3403 & -6.40^{+0.08}_{-0.07} & -25.86^{+0.14}_{-0.12} & -3.61^{+0.21}_{-0.22} & -1.60^{+0.05}_{-0.04} \\
    2.55$^a$ & 2.50 & 2.60 & 2640 & 2640 & -6.15^{+0.08}_{-0.08} & -25.34^{+0.17}_{-0.16} & -3.32^{+0.15}_{-0.16} & -1.39^{+0.08}_{-0.07} \\
    2.65$^a$ & 2.60 & 2.70 & 1883 & 1883 & -5.98^{+0.05}_{-0.06} & -25.15^{+0.13}_{-0.14} & -3.12^{+0.12}_{-0.12} & -1.05^{+0.09}_{-0.08} \\
    2.75$^a$ & 2.70 & 2.80 & 1135 & 1135 & -6.29^{+0.08}_{-0.07} & -25.94^{+0.15}_{-0.13} & -3.78^{+0.27}_{-0.30} & -1.34^{+0.07}_{-0.06} \\
    2.85$^a$ & 2.80 & 2.90 & 1069 & 1069 & -6.45^{+0.11}_{-0.10} & -26.22^{+0.21}_{-0.18} & -3.61^{+0.35}_{-0.41} & -1.46^{+0.08}_{-0.07} \\
    2.95$^a$ & 2.90 & 3.00 & 1104 & 1104 & -6.76^{+0.07}_{-0.06} & -26.53^{+0.11}_{-0.09} & -5.05^{+0.59}_{-0.63} & -1.71^{+0.05}_{-0.04} \\
    3.05$^a$ & 3.00 & 3.10 & 1127 & 1127 & -6.77^{+0.08}_{-0.07} & -26.48^{+0.12}_{-0.11} & -4.68^{+0.44}_{-0.52} & -1.70^{+0.06}_{-0.05} \\
    3.15$^a$ & 3.10 & 3.20 & 1041 & 1041 & -7.26^{+0.16}_{-0.11} & -27.11^{+0.22}_{-0.17} & -4.38^{+0.76}_{-1.30} & -1.96^{+0.07}_{-0.05} \\
    3.25$^a$ & 3.20 & 3.30 & 815 & 815 & -7.34^{+0.13}_{-0.13} & -27.20^{+0.20}_{-0.22} & -4.39^{+0.69}_{-0.79} & -1.94^{+0.06}_{-0.05} \\
    3.34$^a$ & 3.30 & 3.40 & 510 & 510 & -7.54^{+0.21}_{-0.21} & -27.39^{+0.28}_{-0.37} & -4.67^{+1.38}_{-1.44} & -2.08^{+0.09}_{-0.07} \\
    3.44$^a$ & 3.40 & 3.50 & 155 & 155 & -6.76^{+0.19}_{-0.20} & -26.62^{+0.40}_{-0.36} & -3.67^{+0.62}_{-0.83} & -1.24^{+0.28}_{-0.23} \\
    3.88 & 3.70 & 4.10 & 628 & 1204 & -7.91^{+0.11}_{-0.11} & -27.26^{+0.13}_{-0.12} & -4.83^{+0.33}_{-0.38} & -2.07^{+0.10}_{-0.09} \\
    4.35 & 4.10 & 4.70 & 442 & 603 & -8.32^{+0.29}_{-0.25} & -27.37^{+0.37}_{-0.30} & -4.20^{+0.41}_{-0.50} & -2.21^{+0.15}_{-0.13} \\
    4.92 & 4.70 & 5.50 & 263 & 263 & -9.02^{+0.30}_{-0.21} & -27.89^{+0.37}_{-0.26} & -4.58^{+0.71}_{-0.80} & -2.30^{+0.11}_{-0.08} \\
    6.00 & 5.50 & 6.50 & 66 & 66 & -10.66^{+0.74}_{-1.11} & -29.21^{+1.08}_{-1.89} & -5.05^{+0.76}_{-1.18} & -2.41^{+0.10}_{-0.08} \\
    \hline
  \end{tabular}\\
  \begin{minipage}{13.0cm}
    \textsuperscript{$a$}{Redshift bin not considered in the joint QLF fit due to systematic errors (open circles in Figure~\ref{fig:evoln}).}
  \end{minipage}
\end{table*}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.7\textwidth]{evolution_global.pdf}
    % summary_fromFile.py 
  \end{center}
  \caption{Luminosity function parameter evolution in the global
    models.  The symbols show the posterior median values of
    parameters with one-sigma (68.26\%) uncertainties in redshift bins
    from Figure~\ref{fig:evoln}.  Redshift bins deemed to be affected
    by systematics and removed from the global analysis are shown by
    the grey open circles.  In each panel, the solid curves and shaded
    regions show the three derived global models with one-sigma
    uncertainties.  Model~1 provides a better fit, but requires a
    rapid change in the faint-end slope at $z\sim 3.5$.}
  \label{fig:evoln_global}
\end{figure*}

@@

We thank Eilat Glikman, Linhua Jiang, Nobunari Kashi\-kawa, Ian
McGreer, Nick Ross, Chris Willott, and Jinyi Yang for sharing data and
especially for sharing their quasar selection functions.  It is a
pleasure to acknowledge useful discussions with James Aird, Eduardo
Ba\~nados, Manda Banerji, Tirthankar Roy Choudhury, George Efstathiou,
Xiaohui Fan, Andrea Ferrara, Prakash Gaikwad, Francesco Haardt, Martin
Haehnelt, Paul Hewett, David Hogg, Vikram Khaire, Sergey Koposov,
Donald Lynden-Bell, Roberto Maiolino, Richard McMahon, Daniel
Mortlock, Ewald Puchwein, Gordon Richards, Alberto Rorai, Bram
Venemans and Stephen Warren.  GK acknowledges support from ERC
Advanced Grant 320596 `The Emergence of Structure During the Epoch of
Reionization'.

>>>>

    &
    &
    &
    &
    &
    \multicolumn{1}{c}{cMpc$^{-3}$mag$^{-1}$)} &
    &
    & \\
    \hline
    0.31$^a$ & 0.10 & 0.40 & 3520 & 3632 & -5.72^{+0.08}_{-0.12} & -21.30^{+0.24}_{-0.29} & -2.74^{+0.09}_{-0.11} & -1.07^{+0.22}_{-0.20} \\
    0.50$^a$ & 0.40 & 0.60 & 4555 & 4686 & -6.39^{+0.05}_{-0.05} & -23.38^{+0.10}_{-0.09} & -3.49^{+0.10}_{-0.10} & -1.55^{+0.04}_{-0.04} \\
    0.72 & 0.60 & 0.80 & 3308 & 4684 & -6.57^{+0.14}_{-0.12} & -24.21^{+0.22}_{-0.18} & -3.55^{+0.16}_{-0.17} & -1.89^{+0.06}_{-0.05} \\
    0.91 & 0.80 & 1.00 & 3922 & 5248 & -6.48^{+0.11}_{-0.10} & -24.60^{+0.16}_{-0.14} & -3.69^{+0.12}_{-0.13} & -1.88^{+0.07}_{-0.05} \\
    1.10 & 1.00 & 1.20 & 6367 & 6566 & -6.62^{+0.03}_{-0.03} & -25.24^{+0.05}_{-0.05} & -4.24^{+0.09}_{-0.09} & -1.84^{+0.02}_{-0.02} \\
    1.30 & 1.20 & 1.40 & 6479 & 7132 & -6.52^{+0.04}_{-0.04} & -25.41^{+0.06}_{-0.06} & -4.02^{+0.09}_{-0.09} & -1.88^{+0.03}_{-0.03} \\
    1.50 & 1.40 & 1.60 & 7539 & 7771 & -6.59^{+0.03}_{-0.03} & -25.77^{+0.04}_{-0.04} & -4.35^{+0.09}_{-0.09} & -1.87^{+0.02}_{-0.02} \\
    1.71 & 1.60 & 1.80 & 6788 & 7421 & -6.29^{+0.04}_{-0.04} & -25.56^{+0.06}_{-0.06} & -3.94^{+0.07}_{-0.08} & -1.69^{+0.03}_{-0.03} \\
    1.98 & 1.80 & 2.20 & 10478 & 1087& -6.79^{+0.03}_{-0.03} & -26.35^{+0.04}_{-0.04} & -4.26^{+0.07}_{-0.08} & -1.98^{+0.02}_{-0.02} \\
    2.30$^a$ & 2.20 & 2.40 & 8419 & 8419 & -6.16^{+0.07}_{-0.06} & -25.50^{+0.12}_{-0.11} & -3.34^{+0.11}_{-0.12} & -1.61^{+0.04}_{-0.04} \\
    2.45$^a$ & 2.40 & 2.50 & 3403 & 3403 & -6.40^{+0.08}_{-0.08} & -25.86^{+0.14}_{-0.13} & -3.61^{+0.21}_{-0.22} & -1.60^{+0.05}_{-0.04} \\
    2.55$^a$ & 2.50 & 2.60 & 2640 & 2640 & -6.15^{+0.08}_{-0.08} & -25.33^{+0.17}_{-0.16} & -3.31^{+0.15}_{-0.16} & -1.38^{+0.08}_{-0.07} \\
    2.65$^a$ & 2.60 & 2.70 & 1883 & 1883 & -5.98^{+0.05}_{-0.06} & -25.16^{+0.13}_{-0.13} & -3.13^{+0.11}_{-0.12} & -1.05^{+0.08}_{-0.08} \\
    2.75$^a$ & 2.70 & 2.80 & 1135 & 1135 & -6.29^{+0.07}_{-0.07} & -25.94^{+0.14}_{-0.13} & -3.78^{+0.26}_{-0.29} & -1.34^{+0.07}_{-0.06} \\
    2.85$^a$ & 2.80 & 2.90 & 1069 & 1069 & -6.46^{+0.12}_{-0.10} & -26.22^{+0.23}_{-0.18} & -3.61^{+0.37}_{-0.43} & -1.46^{+0.08}_{-0.07} \\
    2.95$^a$ & 2.90 & 3.00 & 1104 & 1104 & -6.76^{+0.07}_{-0.06} & -26.52^{+0.11}_{-0.09} & -5.01^{+0.58}_{-0.64} & -1.71^{+0.05}_{-0.04} \\
    3.05$^a$ & 3.00 & 3.10 & 1127 & 1127 & -6.77^{+0.08}_{-0.07} & -26.48^{+0.11}_{-0.10} & -4.72^{+0.44}_{-0.50} & -1.70^{+0.06}_{-0.05} \\
    3.15$^a$ & 3.10 & 3.20 & 1041 & 1041 & -7.25^{+0.15}_{-0.12} & -27.10^{+0.21}_{-0.18} & -4.39^{+0.75}_{-1.18} & -1.96^{+0.07}_{-0.05} \\
    3.25$^a$ & 3.20 & 3.30 & 815 & 815 &  -7.33^{+0.12}_{-0.13} & -27.19^{+0.19}_{-0.21} & -4.39^{+0.66}_{-0.76} & -1.93^{+0.06}_{-0.05} \\
    3.34$^a$ & 3.30 & 3.40 & 510 & 510 &  -7.54^{+0.22}_{-0.22} & -27.39^{+0.29}_{-0.37} & -4.76^{+1.29}_{-1.38} & -2.08^{+0.09}_{-0.07} \\
    3.44 & 3.40 & 3.50 & 155 & 155 &  -6.78^{+0.20}_{-0.20} & -26.65^{+0.44}_{-0.34} & -3.72^{+0.68}_{-0.89} & -1.25^{+0.29}_{-0.22} \\
    3.88 & 3.70 & 4.10 & 628 & 1204 & -7.92^{+0.12}_{-0.10} & -27.26^{+0.14}_{-0.12} & -4.84^{+0.36}_{-0.38} & -2.07^{+0.10}_{-0.09} \\
    4.35 & 4.10 & 4.70 & 442 & 603 &  -8.32^{+0.31}_{-0.26} & -27.37^{+0.39}_{-0.32} & -4.19^{+0.43}_{-0.50} & -2.20^{+0.16}_{-0.14} \\
    4.92 & 4.70 & 5.50 & 263 & 263 &  -9.03^{+0.29}_{-0.22} & -27.89^{+0.36}_{-0.26} & -4.55^{+0.69}_{-0.82} & -2.31^{+0.11}_{-0.09} \\
    6.00 & 5.50 & 6.50 & 66 & 66 &  -10.66^{+0.75}_{-1.12} & -29.19^{+1.09}_{-1.89} & -5.00^{+0.73}_{-1.20} & -2.40^{+0.09}_{-0.08} \\
    \hline
  \end{tabular}\\
  \begin{minipage}{13.0cm}
    \textsuperscript{$a$}{Redshift bin not considered in the joint QLF fit due to systematic errors (open circles in Figure~\ref{fig:evoln}).}
  \end{minipage}
\end{table*}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.7\textwidth]{evolution_global.pdf}
    % summary_fromFile.py 
  \end{center}
  \caption{Luminosity function parameter evolution in the global
    models.  The symbols show the posterior median values of
    parameters with one-sigma (68.26\%) uncertainties in redshift bins
    from Figure~\ref{fig:evoln}.  Redshift bins deemed to be affected
    by systematics and removed from the global analysis are shown by
    the grey open circles.  In each panel, the solid curves and shaded
    regions show the three derived global models with one-sigma
    uncertainties.}
  \label{fig:evoln_global}
\end{figure*}

@@

We thank Eilat Glikman, Linhua Jiang, Nobunari Kashi\-kawa, Ian
McGreer, Nick Ross, Chris Willott, and Jinyi Yang for sharing data and
especially for sharing their quasar selection functions.  It is a
pleasure to acknowledge useful discussions with James Aird, Eduardo
Ba\~nados, Manda Banerji, Tirthankar Roy Choudhury, George Efstathiou,
Xiaohui Fan, Andrea Ferrara, Prakash Gaikwad, Francesco Haardt, Martin
Haehnelt, Paul Hewett, David Hogg, Vikram Khaire, Sergey Koposov,
Donald Lynden-Bell, Roberto Maiolino, Richard McMahon, Daniel
Mortlock, Ewald Puchwein, Gordon Richards, Alberto Rorai, Bram
Venemans and Stephen Warren.  \new{We thank the anonymous referee for
  their comments.} GK acknowledges support from ERC Advanced Grant
320596 `The Emergence of Structure During the Epoch of Reionization'.
